---
title: "Untitled"
format: html
---

```{r}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2022-07-12")
flights <- tt$flights

```


# Readme

Take a look at the readme for the weekly data to get insight on the dataset.
This includes a data dictionary, source, and a link to an article on the data.

```{r Readme, eval = interactive()}

tt

```


# Glimpse Data

Take an initial look at the format of the data available.

```{r Glimpse}

tt %>% 
  map(glimpse)

```

# Wrangle

Explore the data and process it into a nice format for plotting! Access each dataset by name by using a dollarsign after the `tt` object and then the name of the data set.

```{r Wrangle}

flights %>% view()

df <- flights %>% 
  janitor::clean_names()

```

Number of flights per day

```{r}
df_sum <- df %>% 
  group_by(flt_date, pivot_label) %>% 
  summarise(total_flights = sum(flt_tot_1)) %>% 
  ungroup()

small_group <- df_sum %>% distinct(pivot_label) %>% sample_n(30)

df_sum %>% 
  filter(pivot_label %in% small_group$pivot_label) %>% 
  ggplot(aes(total_flights))
```


# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}


  
```

# Save Image

Save your image for sharing. Be sure to use the `#TidyTuesday` hashtag in your post on twitter! 

```{r}

# This will save your most recent plot
ggsave(
  filename = "My TidyTuesday Plot.png",
  device = "png")

```
